Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-08 paper/main.tex
Updates

\subsection{Using LLMs as Experts}
Recently, there has been a lot of work towards using LLMs for causal discovery,
with tasks ranging from determining pairwise edge orientation
\citep{Kiciman2023, Jin2024} to full causal structure learning \citep{Naik2023,
Vashishtha2023} and counterfactual reasoning tasks\citep{Kiciman2023} (see
\citet{Liu2024} for an overview).

@@

\section{Web Tool}
\label{sec:web}
To enable users to apply this method to their own datasets, we developed an
interactive web-based tool (shown in Fig.~\ref{fig:web}) for constructing
models. Users begin by uploading their dataset, which initializes an empty DAG
with nodes corresponding to the dataset\'s variables. They can then specify a
p-value threshold and a measure of association threshold.

@@

\begin{figure}[t!]
	\centering
	\includegraphics[page=1]{fig5.pdf}
	\caption{DAG learned using the adult income dataset using an LLM (GEMINI-1.5-flash) as the expert. The p-value threshold used is $ 0.05 $ and the measure of association threshold is $ 0. 1 $}
	\label{fig:adult_llm}
\end{figure}

>>>>

\subsection{Using LLMs as Experts}

\begin{figure}[t!]
	\centering
	\includegraphics[page=1]{fig5.pdf}
	\caption{DAG learned from the adult income dataset using an LLM (GEMINI-1.5-flash) as the expert. The p-value threshold used is $ 0.05 $ and the measure of association threshold is $ 0. 1 $}
	\label{fig:adult_llm}
\end{figure}
Recently, there has been a lot of work towards using LLMs for causal discovery,
with tasks ranging from determining pairwise edge orientation
\citep{Kiciman2023, Jin2024} to full causal structure learning \citep{Naik2023,
Vashishtha2023} and counterfactual reasoning tasks\citep{Kiciman2023} (see
\citet{Liu2024} for an overview).

@@

\section{Web Tool}
\label{sec:web}

To enable users to apply this method to their own datasets, we developed an
interactive web-based tool (shown in Fig.~\ref{fig:web}) for constructing
models. Users begin by uploading their dataset, which initializes an empty DAG
with nodes corresponding to the dataset\'s variables. They can then specify a
p-value threshold and a measure of association threshold.

@@
